---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# synopticr

<!-- badges: start -->

[![R-CMD-check](https://github.com/andypicke/synopticr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/andypicke/synopticr/actions/workflows/R-CMD-check.yaml) [![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)

<!-- badges: end -->

The goal of {synopticr} is to make it easy to retrieve weather data from the [Synoptic Data](https://synopticdata.com/) [weather API](https://synopticdata.com/weatherapi/) via R.

## Installation

You can install the development version of {synopticr} from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andypicke/synopticr")
```

## Authentication

You will need to [sign up for an api token](https://signin.synopticdata.com/u/signup/) before using the api. Synoptic offers free [open-access](https://synopticdata.com/pricing/open-access-pricing/) for non-commercial users. The functions in {synopticr} assume by default that your token is stored in your *.Renviron* file as SYNOPTIC_API_KEY="you_key_here". You can also pass in your api token explicitly if wanted.

::: callout-note
To store your api key, I find the easiest way is to use the *edit_r_environ()* function from the {usethis} package.
:::


# Examples


### Get networks

The *get_networks()* function returns a dataframe of all the weather station networks available through the Synoptic api. 

```{r}

library(synopticr)

networks <- get_networks()

str(networks)

```


### Get station metadata

The *get_metadata()* function will return a dataframe of stations and their metadata for a specified state. 

- Note the *STID* for each station can be used in other functions to request data for a specific station.

```{r }


meta <- get_metadata(wh_state = "MA")

#head(meta)
str(meta)

```

### Get latest data *In Progress*

*get_latest_data()* returns the latest available data for stations in 1 state.

- Each row in the returned dataframe corresponds to a single station.

- *I am currently working on improving this function to clean up the variable names and add more options (requesting data for single stations etc.)*

```{r}

df <- get_latest_data(wh_state = "MA")

library(dplyr)

str(df)


```

